Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-02 paper/paper.tex
fix typos

The nondeterministic operator @nd@ is also slightly rewrite to cache-passing style:
continuation @k@ takes an additional argument of type @Cache@; the current accumulated
cache @acc.cache@ is exposed to @k@ when applies.

>>>>

The nondeterministic operator @nd@ is also slightly rewritten to cache-passing style:
the continuation @k@ takes an additional argument of type @Cache@; the current accumulated
cache @acc.cache@ is exposed to @k@ when applied.
